---
title: "220412.exercise.challenge"
author: "Karim Primov"
date: "4/12/2022"
output: html_document
---

```{r}
library(tidyverse)
library(mosaic)
library(car)
library(broom)
library(ggplot2)
library(infer)
library(dplyr)
```

```{r}
f <- "https://raw.githubusercontent.com/difiore/ada-2022-datasets/main/AVONETdataset1.csv"
d <- read_csv(f, col_names = TRUE)
names(d)
```

Keeping these 19 variables:
```{r}
df <- d %>%
  select(Species1, Family1, Order1, Beak.Length_Culmen, Beak.Width, Beak.Depth, Tarsus.Length, Wing.Length, Tail.Length, Mass, Habitat, Migration, Trophic.Level, Trophic.Niche, Primary.Lifestyle, Min.Latitude, Max.Latitude, Centroid.Latitude, Range.Size)

```

Relative Beak length
```{r}
rel.beak.length <- lm(data = df, log(Beak.Length_Culmen) ~ log(Mass))
rel.beak.length$residuals
```

Relative Tarsus Length 
```{r}
rel.tarsus.length <- lm(data = df, log(Tarsus.Length) ~ log(Mass))
rel.tarsus.length$residuals
```


Mutating relative beak length and relative tarsus length to dataframe "df" into new dataframe "df"
```{r}
df <- df %>%
  mutate(Relative.Beak.Length = rel.beak.length$residuals) %>%
  mutate(Relative.Tarsus.Length = rel.tarsus.length$residuals)
```

Boxplot of relative tarsus length by primary lifestyle
```{r}
boxplot.tarsus.lifestyle <- ggplot(df, aes(x = Primary.Lifestyle, y = Relative.Tarsus.Length)) + geom_boxplot()
boxplot.tarsus.lifestyle
```

Boxplot of relative beak length by trophic niche
```{r}
boxplot.beak.niche <- ggplot(df, aes(x = Trophic.Niche, y = Relative.Beak.Length)) + geom_boxplot()
boxplot.beak.niche
```
Run ANOVA to look at association between geographic range size and migratory status 
```{r}
grs.mig.aov <- aov(data = df, Range.Size ~ Migration)
summary(grs.mig.aov)
```


Limit data to Passeriformes

Filtering dataframe 

```{r}
df.pass <- df %>%
  filter(Order1 == "Passeriformes")
```


ANOVA looking at association between relative beak length and primary lifestyle 
```{r}
rbl.pl.aov <- aov(data = df.pass, Relative.Beak.Length ~ Primary.Lifestyle) 
summary(rbl.pl.aov)
```

ANOVA looking at association between relative beak length and trophic level  
```{r}
rbl.tl.aov <- aov(data = df.pass, Relative.Beak.Length ~ Trophic.Level)
summary(rbl.tl.aov)
```


```{r}
boxplot.beak.troph.level <- ggplot(df, aes(x = Trophic.Level, y = Relative.Beak.Length)) + geom_boxplot()
boxplot.beak.troph.level
```
#facet-wrapping
```{r}
boxplot.beak.primary.lifestyle <- ggplot(df, aes(x = Primary.Lifestyle, y = Relative.Beak.Length)) + geom_boxplot()
boxplot.beak.primary.lifestyle
```

Combined Effects of predictors (primary lifestyle and trophic level)
```{r}
p <- ggplot(data=df, aes(x = Relative.Beak.Length, y = Primary.Lifestyle)) + geom_boxplot() +
  facet_wrap(~Trophic.Level, ncol=1) +
  xlab("Relative Beak Length") + ylab("Primary Lifestyle")
# and let's plot what the data look like
# p <- p + geom_point() # uncommenting this shows all points
p <- p + stat_summary(data=df, aes(x = Relative.Beak.Length, y = Primary.Lifestyle),
  fun = base::mean,
  # make sure we use {base} version of mean
  color = "darkgreen", geom = "point", shape = 8, size = 6)
p
```
Step 5:
```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```